---
title: "sangeranalyseR"
author: "Author: Kuan-Hao Chao (u7022787@anu.edu.au)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  BiocStyle::html_document:
    toc_float: true
    code_folding: show
    fig_caption: yes
  BiocStyle::pdf_document: default
#bibliography: bibliography.bib
params:
  SangerRead: NULL
  outputDir: ""
  showChromatogram: FALSE
fontsize: 14pt
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\usepackage[utf8]{inputenc}
---

# sangeranalyseR 'SangerRead' Report

```{r}
library(sangeranalyseR)
```

## Basic Project Information:

<details><summary>CLICK ME</summary>

<ul style="list-style-type:disc;">
  <li>**Output Directory : **  <span class="tab">*`r params$outputDir`*</span></li>

  <li>**Input Directory : **  <span class="tab"><i>`r dirname(params$SangerRead@readFileName)`</i></span></li>

  <li>**Input Filename : **  <span class="tab"><i>`r basename(params$SangerRead@readFileName)`</i></span></li>

  <li>**Read Feature : **  <span class="tab">*`r params$SangerRead@readFeature`*</span></li>
</ul>

</details>

## Quality Trimming

<details><summary>CLICK ME</summary>

<ul style="list-style-type:disc;">

`r if(params$SangerRead@QualityReport@TrimmingMethod == "M1"){"<li>**Trimming Method**: <span class='tab'><i> Method 1 'Logarithmic Scale Trimming' </i></span></li>"}`

`r if(params$SangerRead@QualityReport@TrimmingMethod == "M2"){"<li>**Trimming Method**: <span class='tab'><i> Method 2 'Logarithmic Scale Sliding Window Trimming' </i></span></li>"}`

`r if(params$SangerRead@QualityReport@TrimmingMethod == "M1"){paste("<li>**M1 Trimming Cutoffe**: <span class='tab'><i>", params$SangerRead@QualityReport@M1TrimmingCutoff, "</i></span></li>")}`

`r if(params$SangerRead@QualityReport@TrimmingMethod == "M2"){paste("<li>**M2 Cutoff Quality Score**: <span class='tab'><i>", params$SangerRead@QualityReport@M2CutoffQualityScore, "</i></span></li>")}`

`r if(params$SangerRead@QualityReport@TrimmingMethod == "M2"){paste("<li>**M2 Cutoff Quality Score**: <span class='tab'><i>", params$SangerRead@QualityReport@M2SlidingWindowSize, "</i></span></li>")}`

  <li>**Raw Sequence Length**:  <span class="tab">*`r params$SangerRead@QualityReport@rawSeqLength`*</span></li>
  
  <li>**Trimmed Sequence Length**:  <span class="tab">*`r params$SangerRead@QualityReport@trimmedSeqLength`*</span></li>
  
  <li>**Trimmed Start Point**:  <span class="tab">*`r params$SangerRead@QualityReport@trimmedStartPos`*</span></li>
  
  <li>**Trimmed End Point**:  <span class="tab">*`r params$SangerRead@QualityReport@trimmedFinishPos`*</span></li>
  
  <li>**Raw Mean Quality Score**:  <span class="tab">*`r params$SangerRead@QualityReport@rawMeanQualityScore`*</span></li>

  <li>**Trimmed Mean Quality Score**:  <span class="tab">*`r params$SangerRead@QualityReport@trimmedMeanQualityScore`*</span></li>
  
  <li>**Raw Min Quality Score**:  <span class="tab">*`r params$SangerRead@QualityReport@rawMinQualityScore`*</span></li>
  
  <li>**Trimmed Min Quality Score**: <span class="tab">*`r params$SangerRead@QualityReport@trimmedMinQualityScore`*</span></li>
  
  <li>**Remaining Read Ratio**: <span class="tab">*`r params$SangerRead@QualityReport@remainingRatio`*</span></li>

</ul>

```{r}
qualityBasePlot(params$SangerRead)
```

</details>

  
  <li>**Phred Scores**:  <span class="tab">*`r params$SangerRead@QualityReport@qualityPhredScores`*</span></li>
--- 

## Chromatogram
<details><summary>CLICK ME</summary>
</details>





<details><summary>CLICK ME</summary>
## yes, even hidden code blocks!
```{r}
print(params$SangerRead@readFileName)
```
</details>

# Second
`r if(params$showChromatogram){"# Show chromatogram !!!"}`







<style>


li{
    margin-top: 16px;
}

li:first-child {
    margin-top:0;
}

.tab {position:absolute;left:350px; }

}
</style>


