---
title: "An Introduction to sangeranalyseR"
author: "Author: Kuan-Hao Chao (u7022787@anu.edu.au)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  BiocStyle::html_document:
    toc_float: true
    code_folding: show
    fig_caption: yes
  BiocStyle::pdf_document: default
#bibliography: bibliography.bib
fontsize: 14pt
vignette: >
  %\VignetteIndexEntry{sangeranalyseR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\usepackage[utf8]{inputenc}
  %\VignettePackage{sangeranalyseR}
---
```{r style, echo=FALSE, results="asis", message=FALSE}
BiocStyle::markdown()
knitr::opts_chunk$set(tidy = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
library(sangeranalyseR)
```

# Introduction
[sangeranalyseR](https://github.com/roblanf/sangeranalyseR) is an R package that provides fast, flexible, and reproducible workflows for assembling your sanger seuqencing data into contigs. It adds to a list of already widely-used tools, like Geneious, CodonCode Aligner and Phred-Phrap-Consed;. What makes it different from these tools is that it’s free, it’s open source, and it’s in R.

For more information, please check our 📒[sangeranalyseR documentation](https://sangeranalyser.readthedocs.io/en/latest/#).


