---
title: "An Introduction to sangeranalyseR"
author: "Kuan-Hao Chao (ntueeb05howard@gmail.com)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output:
  BiocStyle::html_document:
    toc_float: true
    code_folding: show
    fig_caption: yes
  BiocStyle::pdf_document: default
fontsize: 14pt
vignette: >
  %\VignetteIndexEntry{sangeranalyseR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\usepackage[utf8]{inputenc}
  %\VignettePackage{sangeranalyseR}
---
```{r style, echo=FALSE, results="asis", message=FALSE}
BiocStyle::markdown()
knitr::opts_chunk$set(tidy = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      eval = FALSE)
```

```{r setup}
library(sangeranalyseR)
```

# Introduction

[sangeranalyseR](https://github.com/roblanf/sangeranalyseR) is an R package that
provides fast, flexible, and reproducible workflows for assembling Sanger
sequencing data into contigs. It is a free, open-source alternative to Geneious,
CodonCode Aligner, and Phred-Phrap-Consed. The full reference manual is on the
[ReadTheDocs site](https://sangeranalyser.readthedocs.io/en/latest/); this
vignette focuses on the *recipes* most users actually need: how to call the
constructors, what each parameter does, and how to interpret the output.

The package is built around three S4 classes that form a containment hierarchy:

```
SangerAlignment   ← a set of contigs aligned to each other
└── SangerContig  ← one assembled contig (forward + reverse reads)
    └── SangerRead ← one ABIF or FASTA read
```

# How to … (recipe gallery)

Every recipe uses the bundled `Allolobophora chlorotica` ABIF fixture (8 reads
arranged into 4 forward+reverse pairs). The `system.file()` call below works
from any installed copy of the package.

```{r locate-fixture}
ab1_dir <- system.file("extdata", "Allolobophora_chlorotica", "ACHLO",
                       package = "sangeranalyseR")
list.files(ab1_dir, pattern = "\\.ab1$")
```

## How to assemble a single contig

```{r recipe-single-contig}
sc <- SangerContig(
    inputSource         = "ABIF",
    processMethod       = "REGEX",
    ABIF_Directory      = ab1_dir,
    contigName          = "Achl_ACHLO006-09",
    REGEX_SuffixForward = "_[0-9]*_F\\.ab1$",
    REGEX_SuffixReverse = "_[0-9]*_R\\.ab1$",
    TrimmingMethod      = "M1",
    M1TrimmingCutoff    = 0.0001
)
sc@objectResults@creationResult        # TRUE
length(sc@forwardReadList)              # 1 forward read
length(sc@reverseReadList)              # 1 reverse read
as.character(sc@contigSeq)              # the consensus sequence
```

## How to assemble many contigs at once (`SangerAlignment`)

```{r recipe-alignment}
sa <- SangerAlignment(
    inputSource         = "ABIF",
    processMethod       = "REGEX",
    ABIF_Directory      = ab1_dir,
    REGEX_SuffixForward = "_[0-9]*_F\\.ab1$",
    REGEX_SuffixReverse = "_[0-9]*_R\\.ab1$",
    TrimmingMethod      = "M1"
)
length(sa@contigList)                  # 4 contigs
length(sa@contigsConsensus)            # cross-contig consensus length
```

## How to use a CSV mapping instead of regex

When your filenames don't follow a clean `_F.ab1` / `_R.ab1` convention, supply
a `reads,direction,contig` CSV that explicitly maps every read:

```{r recipe-csv}
csv_path <- system.file("extdata", "ab1", "SangerAlignment",
                        "names_conversion.csv", package = "sangeranalyseR")
sa_csv <- SangerAlignment(
    inputSource         = "ABIF",
    processMethod       = "CSV",
    ABIF_Directory      = ab1_dir,
    CSV_NamesConversion = csv_path
)
```

Phase-15 fix: contig labels in the CSV no longer have to appear as substrings
of filenames. The CSV's `reads` column drives the lookup directly.

## How to handle forward-only (or reverse-only) datasets

Common in 16S barcoding and short-read survey pipelines. Pass `NULL` (or
`NA_character_`) for the missing-direction suffix and set `minReadsNum = 1` so
each surviving read can become its own contig:

```{r recipe-forward-only}
sa_fwd <- SangerAlignment(
    inputSource         = "ABIF",
    processMethod       = "REGEX",
    ABIF_Directory      = ab1_dir,
    REGEX_SuffixForward = "_[0-9]*_F\\.ab1$",
    REGEX_SuffixReverse = NULL,        # explicit forward-only (Phase-15)
    minReadsNum         = 1
)
```

## How to deal with low-quality / short reads

Two trimming algorithms, controlled by `TrimmingMethod`:

| Method | Algorithm                                          | Parameters                                           |
| ------ | -------------------------------------------------- | ---------------------------------------------------- |
| `"M1"` | Modified Mott's (Phred/Phrap-style cumulative)     | `M1TrimmingCutoff` (probability; default `0.0001`)   |
| `"M2"` | Sliding-window mean Phred (Trimmomatic-style)      | `M2CutoffQualityScore`, `M2SlidingWindowSize`        |

Tighter trimming for noisy data:

```{r recipe-strict-trim}
sa_strict <- SangerAlignment(
    inputSource          = "ABIF",
    processMethod        = "REGEX",
    ABIF_Directory       = ab1_dir,
    REGEX_SuffixForward  = "_[0-9]*_F\\.ab1$",
    REGEX_SuffixReverse  = "_[0-9]*_R\\.ab1$",
    TrimmingMethod       = "M2",
    M2CutoffQualityScore = 30,
    M2SlidingWindowSize  = 15,
    minReadLength        = 50      # post-trim length floor
)
```

Phase-16 added a defensive width filter: any read trimmed to < 2 bp is
silently dropped before alignment with a `MIN_READ_LENGTH_DEFENSIVE_DROP`
warning, so you never see `DECIPHER::AlignSeqs` crash on degenerate inputs.

## How to detect spurious low-overlap merges

Forward + reverse reads with poor overlap silently produce IUPAC-ambiguity-soup
consensus. Phase-16 adds an opt-in alignment-quality check:

```{r recipe-overlap-check}
sa_overlap <- SangerAlignment(
    inputSource         = "ABIF",
    processMethod       = "REGEX",
    ABIF_Directory      = ab1_dir,
    REGEX_SuffixForward = "_[0-9]*_F\\.ab1$",
    REGEX_SuffixReverse = "_[0-9]*_R\\.ab1$",
    minOverlapBases     = 50L,        # warn if any pairwise overlap < 50 bp
    minOverlapFraction  = 0.05        # or < 5% of the shorter read
)
```

When triggered, you'll see `LOW_OVERLAP_WARN` in the log alongside the offending
read pair.

## How to choose a consensus base-calling method

Three modes are exposed via `consensusMethod`:

| Mode                      | Behaviour                                                                                          | Per-position quality |
| ------------------------- | -------------------------------------------------------------------------------------------------- | --------------------- |
| `"strict"` (default)      | DECIPHER's `ConsensusSequence` with IUPAC ambiguity codes for disagreements.                       | not provided          |
| `"majority"`              | Per-column plurality vote; ties break alphabetically. No IUPAC codes ever appear in the output.    | synthetic Phred       |
| `"quality_weighted"`      | Same as majority but votes are weighted by source-read Phred. Alias: `qualityAware = TRUE`.        | mean Phred of agreers |

```{r recipe-majority-consensus}
sc_majority <- SangerContig(
    inputSource         = "ABIF",
    processMethod       = "REGEX",
    ABIF_Directory      = ab1_dir,
    contigName          = "Achl_ACHLO006-09",
    REGEX_SuffixForward = "_[0-9]*_F\\.ab1$",
    REGEX_SuffixReverse = "_[0-9]*_R\\.ab1$",
    consensusMethod     = "majority"
)
as.character(sc_majority@contigSeq)        # plain ACGT, no IUPAC codes
attr(sc_majority@contigSeq, "qualityScores")  # per-position synthetic Phred
```

## How to interpret the chromatogram

ABIF files store per-base trace amplitudes for the four channels (A, C, G, T)
and per-base Phred quality scores in the `PCON.2` data block. `sangeranalyseR`
re-runs the base-calling step on those raw traces using the
`MakeBaseCallsInside` helper:

1. Detect peaks per channel (`getpeaks`).
2. For each base position, identify the strongest peak across A/C/G/T using
   `signalRatioCutoff` (default 0.33 — secondary peaks below that fraction of
   the primary peak are dropped).
3. Tied peaks → the IUPAC ambiguity code corresponding to the equally-strong
   bases.
4. Quality scores come from `abifRawData@data$PCON.2` (one entry per detected
   peak).

Visualize either as a static PDF (`chromatogram_overwrite()`) or an interactive
WebGL widget (`chromatogram_plotly()` — Phase-8):

```{r recipe-chromatogram}
sr <- sa@contigList[[1]]@forwardReadList[[1]]
chromatogram_plotly(sr, max_points = 8000, showtrim = TRUE)
```

For very long traces (> 50 k points) the widget downsamples by uniform stride
to keep the browser responsive; the original / rendered point counts are
reported via `attr(p, "downsample_info")`.

## How to deal with secondary peaks

Each `SangerRead` exposes:

* `@primarySeq` — the strongest base at each position (DNAString).
* `@secondarySeq` — the second-strongest base at each position (DNAString).
* `@signalRatioCutoff` (in `@ChromatogramParam`) — the threshold below which a
  secondary peak is dropped.

To inspect secondary peaks within a contig alignment, look at
`sc@secondaryPeakDF` — Phase-3 added one-row-per-ambiguous-column reporting:

```{r recipe-secondary-peaks}
head(sc@secondaryPeakDF)
```

Re-run base-calling with a tighter (or looser) cutoff:

```{r recipe-rebasecall}
sr_re <- MakeBaseCalls(sr, signalRatioCutoff = 0.22)
```

## How to launch the interactive Shiny app

```{r recipe-shiny}
launchApp(sa)             # works on SangerAlignment or SangerContig
```

Per-read trimming sliders, contig overview, alignment browser, FASTA / HTML
report export. Phase-8 also added a lightweight gadget for **batch** trimming
across a whole alignment:

```{r recipe-globaltrim}
sa2 <- globalTrimApp(sa)  # opens a Shiny dialog; returns the re-trimmed SA
```

## How to export results

```{r recipe-export}
out_dir <- tempdir()
writeFasta(sa, outputDir = out_dir)        # SR / SC / SA dispatcher

generateReport(sa, outputDir = out_dir)     # HTML report (requires pandoc)
```

Phase-8 fix: reports now correctly populate the per-frame AA tables under the
default `lazyAA = TRUE` constructor mode (previously the tables silently
rendered empty).

# Constructor parameter reference

Every recipe above is built on three S4 constructors. The full parameter list
is in `?SangerAlignment` / `?SangerContig` / `?SangerRead`; the most-asked-about
groups are summarised below.

## Required parameters (REGEX path)

| Parameter             | What it controls                                                                                  |
| --------------------- | -------------------------------------------------------------------------------------------------- |
| `inputSource`         | `"ABIF"` (raw chromatograms) or `"FASTA"` (pre-called sequences).                                   |
| `processMethod`       | `"REGEX"` (group reads by filename suffix) or `"CSV"` (explicit `reads,direction,contig` mapping). |
| `ABIF_Directory`      | Path to the directory of `.ab1` files. Required for `inputSource = "ABIF"`.                         |
| `FASTA_File`          | Path to a single FASTA file. Required for `inputSource = "FASTA"`.                                  |
| `REGEX_SuffixForward` | A regex matched against forward-read filenames, e.g. `"_F\\.ab1$"`. Pass `NULL` for reverse-only.   |
| `REGEX_SuffixReverse` | A regex matched against reverse-read filenames, e.g. `"_R\\.ab1$"`. Pass `NULL` for forward-only.   |
| `contigName`          | (`SangerContig` only) The label / prefix shared by reads in this contig.                            |
| `CSV_NamesConversion` | Path to a CSV with three columns: `reads`, `direction` (F/R), `contig`. Required for `processMethod = "CSV"`. |

## Trimming parameters

| Parameter              | When used                  | Default        | Notes                                                              |
| ---------------------- | -------------------------- | -------------- | ------------------------------------------------------------------ |
| `TrimmingMethod`        | always                     | `"M1"`          | `"M1"` (modified Mott) or `"M2"` (sliding window).                 |
| `M1TrimmingCutoff`      | `TrimmingMethod = "M1"`     | `0.0001`        | Cumulative probability cutoff. Tighter = more aggressive trim.     |
| `M2CutoffQualityScore`  | `TrimmingMethod = "M2"`     | `20`            | Mean Phred threshold within the sliding window.                    |
| `M2SlidingWindowSize`   | `TrimmingMethod = "M2"`     | `10`            | Width of the sliding window in bp.                                 |
| `minReadLength`         | always                     | `20L`           | Reads trimmed to less than this are dropped from the contig.        |
| `signalRatioCutoff`     | `inputSource = "ABIF"`      | `0.33`          | Secondary peaks below this fraction of the primary peak are dropped. |

## Consensus parameters

| Parameter              | Default      | Notes                                                                                                     |
| ---------------------- | ------------ | --------------------------------------------------------------------------------------------------------- |
| `consensusMethod`      | `"strict"`   | `"strict"` (DECIPHER+IUPAC), `"majority"` (plurality vote, no IUPAC), `"quality_weighted"` (Phred-weighted). |
| `qualityAware`         | `FALSE`      | Shorthand for `consensusMethod = "quality_weighted"`.                                                     |
| `minFractionCall`      | `0.5`        | DECIPHER `minInformation` for `"strict"` mode.                                                            |
| `maxFractionLost`      | `0.5`        | DECIPHER `threshold` for `"strict"` mode.                                                                  |
| `minOverlapBases`       | `0L`         | If > 0, log `LOW_OVERLAP_WARN` when smallest pairwise non-gap overlap < this.                            |
| `minOverlapFraction`    | `0.0`        | Same in fractional terms (overlap as a fraction of the shorter read).                                     |
| `alignSeqsParams`        | `list()`     | Extra named args forwarded to `DECIPHER::AlignSeqs` (e.g. `list(iterations = 1L, refinements = 1L)`).     |

## Performance / parallelism parameters

| Parameter        | Default | Notes                                                                                                                |
| ---------------- | ------- | --------------------------------------------------------------------------------------------------------------------- |
| `processorsNum`   | `1`     | Legacy integer worker count. Honoured for backwards compatibility.                                                    |
| `BPPARAM`         | `NULL`  | Any `BiocParallelParam`. Auto-derived from `processorsNum` if `NULL` (`SerialParam` for 1, `Multicore`/`Snow` for ≥2). |
| `lazyAA`          | `TRUE`  | Skip eager 3-frame AA translation (Phase-6 default; ~35% wall-time saving). Use `primaryAASeqS{1,2,3}()` accessors.    |

# Troubleshooting

| Symptom                                                                          | Cause / fix                                                                                                                                                                                                          |
| -------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| `'qualityPhredScores' length cannot be zero`                                      | ABIF has empty `PCON.2` quality block (older 3500/Beckman firmware). Phase-15 fix: synthesises Phred 30 with `MISSING_QUALITY_SCORES_WARN`. Update to the devel branch.                                              |
| `'REGEX_SuffixReverse' must be character type` on forward-only data              | Phase-15 fix: pass `REGEX_SuffixReverse = NULL` (or `NA_character_`) for forward-only datasets, plus `minReadsNum = 1`.                                                                                              |
| `CONTIG_NUMBER_ZERO_ERROR` even though each `SangerContig()` works individually  | Phase-15 fix: the CSV+ABIF aggregator no longer requires contig labels to be substrings of filenames; the `reads` column drives the lookup.                                                                          |
| `'x' must be an XStringSet object` from `writeFasta` on a single-read contig    | Phase-15 fix: `writeFastaSC` detects empty alignment and writes a single-record FASTA from `@contigSeq`.                                                                                                              |
| Consensus is full of IUPAC ambiguity codes                                       | Phase-17: try `consensusMethod = "majority"` or `"quality_weighted"`. Also check pairwise overlap with `minOverlapBases = 50L` to detect spurious merges.                                                              |
| Reports render with empty AA tables                                              | Phase-8 fix: the RMD templates were reading `@primaryAASeqS*` slots directly under `lazyAA = TRUE`. Fixed in the `devel` branch — use `primaryAASeqS1/S2/S3()` accessors if you customise the templates.            |

# Citation

Please cite the package via:

> Kuan-Hao Chao, Kirston Barton, Sarah Palmer, Robert Lanfear (2021).
> *sangeranalyseR: simple and interactive processing of Sanger sequencing data
> in R.* Genome Biology and Evolution.
> [doi:10.1093/gbe/evab028](https://doi.org/10.1093/gbe/evab028).

# Session info

```{r session-info, eval=TRUE}
sessionInfo()
```
